---
title: "Starter Notebook"
author: "Skylar Pietz"
format: html
execute:
  keep-md: true
---

```{r setup, include = FALSE}
#Load in any packages you need
library(tidyverse)

#Read in any data

```

## Getting Started

You've used Quarto Notebooks a few times already, so you're starting to get the hang of this. Start by editing the Notebook `title:` and make sure you credit yourself as the `author:`. As a reminder, R-code appears in grey chunks throughout your notebook. Anything within these grey blocks must be executable R code. When you are outside of an R chunk, in a section of the notebook with a white background, you can type freely as if you were in a typical Word document.

You'll quickly see the value of including text to explain your code chunks, and motivate your analysis. Trying to get help from a notebook that doesn't effectively use these discussions will be quite difficult. Additionally, future *you* will be very thankful to present-day *you* if you document your analyses well, and will be quick to curse present-day *you* when you do not.

Now, remove this *Getting Started* text and you'll be ready to start sciencing.

# Challenge 1 

```{r}
# Challenge 1

nucleotides <- c("A", "C", "G", "T")
nucleotides

```

# Challenge 2 

```{r}
# Challenge 2

Genome <- 15 
randGenome <- sample(nucleotides, size = Genome, replace = TRUE)
randGenome



```

```{r}
randGenome <- paste(randGenome, collapse = "")
randGenome

```

When I compared my collapsed genome with a classmate, I noticed that we generated very different genomes.

# Challenge 3 

```{r}
# Challenge 3

Genome <- 1500 
randGenome <- sample(nucleotides, size = Genome, replace = TRUE)
randGenome <- paste(randGenome, collapse = "" )
randGenome

```

```{r}
# Challenge 3 continued

set.seed(215)
genomeLength <- 1500

randGenome <- sample(nucleotides, size = genomeLength, replace = TRUE)

randGenome <- paste(randGenome, collapse = "")
randGenome
```

# Challenge 4

```{r}
# Challenge 4

set.seed(215)
Genome <- 100
randGenome <- sample(nucleotides, size = Genome, replace = TRUE)
randGenome <- paste(randGenome, collapse = "")
randGenome

```

The frequency of Adenine (A) in the resulting "genome" above is 23.

```{r}
mySum <- 0

for(i in 1:10){
  mySum <- mySum + i
  print(mySum)
}
```

# Challenge 5 

```{r}
# Challenge 5 

myProduct <- 1
for(j in 1:15){
  myProduct <- myProduct * j
  print(myProduct)
}
  
```

# Challenge 6
